### 2019-12-13 frontmatter.tex
All papers added (missing content). Division of work added.

%-------------------------------------------------------------------------------
% Preface page
%-------------------------------------------------------------------------------
%
\begin{preface}
	This thesis deals with high energy super-lasers. A brief introduction on the
	basic concepts and methods is presented in the first part. The second part
	contains two articles.
	The papers are adjusted to comply with the present thesis format for
	consistency, but their contents have not been altered as compared with their
	original counterparts.
\end{preface}

%-------------------------------------------------------------------------------
% Division of work between authors
%-------------------------------------------------------------------------------
%
\begin{divisionofwork}
	The main advisor for the project is Master Obi-Wan Kenobi (OK).
	Supreme Cancellor Palpatine (DS) acts as co-advisor.

	\paperitem
		The code has been developed by Anakin Skywalker (AS).
		The paper has been written by AS and Darth Vader (DV).

	\paperitem
		The experimental set-up has been designed by DS.
		The simulations have been performed by AS using the control-code
		developed by DS.
		The paper has been written by AS and DV with feedback from OK and DS.

@@

%-------------------------------------------------------------------------------
% Additional publications (comment if none)
%-------------------------------------------------------------------------------
%
\begin{otherpublications}
	The following papers, although related, are not included in this thesis.

  \paperitem%
    {Anakin Skywalker \& Master Obi-Wan Kenobi}% Authors
    {3639}% Year
    {The light sabre: an elegant weapon for a more civilized age}% Title
    {Jedi Journal of Weapons}% Journal
    {33}% Volume
    {2}% Number
    {pp. 55--60}% Pages

\end{otherpublications}

>>>>

%-------------------------------------------------------------------------------
% Preface page
%-------------------------------------------------------------------------------
%
\begin{preface}
	This thesis summarizes a selection of studies on droplet interactions and suspension flows
        that are relevant to applications in microfluidics, soft matter, and rheology.
        A brief introduction of some basic physical concepts and numerical methods is presented in the first part,
        followed by eight journal articles or preprints listed below. 
        For consistency, the papers have been reformated to fit with the style of the thesis;
        their contents have obviously not been altered.
\end{preface}

%-------------------------------------------------------------------------------
% Division of work between authors
%-------------------------------------------------------------------------------
%
\begin{divisionofwork}
	The main thesis advisor is Professor Luca Brandt (LB).
	Associate Professor Outi Tammisola (OT) acts as the co-advisor.

	\paperitem
                LB directed the research.
                Z. Ge (ZG) and J-Ch. Loiseau developed, implemented, and validated the methods.
                OT oversaw the entire project.
		ZG wrote the paper with input from the rest of the authors.

	\paperitem
                A. Leshansky (AL) directed the research.
                I. Fouxon (IF) developed the theory.
		ZG performed the simulation.
                IF wrote the paper with input from the rest of the authors.

	\paperitem
                All authors were involved in the discussion of the research.
		ZG developed the idea, performed the simulation,
                and wrote the paper with input from the rest of the authors.

	\paperitem
                AL directed the research.
                IF constructed the theory.
		B. Rubinstein performed the multipole expansion simulation.
                ZG performed the Navier-Stokes simulation.
                IF wrote the paper with input from the rest of the authors.

	\paperitem
                LB conceived the project.
                M.E. Rosti (MER) implemented the method and performed the simulation.
		ZG performed the droplet statistics and scaling analysis.
                S.S. Jain performed the droplet rendering.
                M.S. Dodd performed the turbulent kinetic budget analysis.
                MER wrote the paper with input from the rest of the authors.

	\paperitem
                G. Kreiss initiated the project.
                H. Holmgren implemented the code and performed part of the Stokes simulation.
                M. Kronbichler performed the phase field simulation.
		ZG performed part of the Stokes simulation, and 
                wrote the paper with input from the rest of the authors.

	\paperitem
                M. Minale and LB directed the research.
                R. Martone and C. Carotenuto performed the experiment.
		ZG performed the simulation with help from R. Radhakrishnan,
                and wrote the paper with input from the rest of the authors.

	\paperitem
                LB led the research.
		ZG developed and implemented the method, with input from OT.
                ZG wrote the paper.

@@

%-------------------------------------------------------------------------------
% Additional publications (comment if none)
%-------------------------------------------------------------------------------
%
%\begin{otherpublications}
%	The following papers, although related, are not included in this thesis.
%
%  \paperitem%
%    {Anakin Skywalker \& Master Obi-Wan Kenobi}% Authors
%    {3639}% Year
%    {The light sabre: an elegant weapon for a more civilized age}% Title
%    {Jedi Journal of Weapons}% Journal
%    {33}% Volume
%    {2}% Number
%    {pp. 55--60}% Pages
%
%\end{otherpublications}
